Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-11-18 manuscript/supplemental_material.Rnw
move GO analysis
remove extra figures from supplemental
 - Remove extra gene trees
 - move analyses up

\subsection{GO Ontology}

@@

@@

\begin{figure}
<<tgfb1.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="TGFB1"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSMODG00000008630","ENSSSCG00000026296"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.3))
@ 
\caption{\genetreeexplanation{\textit{TGFB1}}}
\label{fig:tgfb1_evolution_tree}
\end{figure}

\begin{figure}
<<gpc3.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="GPC3"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSCAFG00000018864","ENSLAFG00000025706"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.13))
@ 
\caption{\genetreeexplanation{\textit{GPC3}}}
\label{fig:gpc3_evolution_tree}
\end{figure}

\subsection{Primate Specific Evolution}

\begin{figure}[hbf]
<<fstl1.evolution.tree,echo=FALSE,out.height="0.6\\textheight",fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="FSTL1"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=5,color="black",fontface="italic")+xlim(0,3))
@ 
\caption{\genetreeexplanation{follistatin-like 1 \textit{FSTL1}}}
\label{fig:fstl1_evolution_tree}
\end{figure}

\subsection{Other Gene Trees}

\begin{figure}[hbf]
<<serpine.evolution.tree,echo=FALSE,out.height="0.6\\textheight",fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="SERPINE2"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSBTAG00000008717",
                                          "ENSMODG00000004913"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=4,color="black",fontface="italic")+xlim(0,0.8))
@ 
\caption{\genetreeexplanation{\textit{SERPINE2}}}
\label{fig:serpine_evolution_tree}
\end{figure}

\begin{figure}
<<sslp1.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_id=="ENSCAFG00000010638" &
                                                    species=="canis familiaris"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,1.2))
@ 
\caption{\genetreeexplanation{\textit{SSLP1}}}
\label{fig:sslp1_evolution_tree}
\end{figure}

\begin{figure}
<<estrogen.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="CYP19A1"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.37))
@ 
\caption{\genetreeexplanation{estrogen synthesis genes}}
\label{fig:estrogen_evolution_tree}
\end{figure}

\begin{figure}
<<progesterone.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="HSD3B1"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSMODG00000005385","ENSLAFG00000027896"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.6))
@ 
\caption{\genetreeexplanation{progesterone synthesis genes}}
\label{fig:progesterone_evolution_tree}
\end{figure}

\begin{figure}
<<chorionic.somatomammotropin.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="CSH1"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.9))
@ 
\caption{\genetreeexplanation{chorionic somatomammotropin}}
\label{fig:csh1_evolution_tree}
\end{figure}

\begin{figure}
<<prolactin.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="PRL"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=3,color="black",fontface="italic")+xlim(0,1))
@ 
\caption{\genetreeexplanation{prolactin}}
\label{fig:prolactin_evolution_tree}
\end{figure}

\begin{figure}
<<rln2.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="RLN2"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.8))
@ 
\caption{\genetreeexplanation{\textit{RLN2}}}
\label{fig:rln2_evolution_tree}
\end{figure}

\begin{figure}
<<ovos2.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_id=="ENSDNOG00000033320"),
                                subtree=c("ENSDNOG00000033320","ENSMODG00000017988"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=5,color="black",fontface="italic")+xlim(0,1.3))
@ 
\caption{\genetreeexplanation{\cow \textit{OVOS2}}}
\label{fig:ovos2_evolution_tree}
\end{figure}

\begin{figure}
<<prolactin.receptor.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="PRLR"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSG00000113494","ENSMODG00000020376"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.3))
@ 
\caption{\genetreeexplanation{prolactin receptor, \textit{PRLR}}}
\label{fig:prolactin_receptor_evolution_tree}
\end{figure}

\begin{figure}
<<hoxa11.receptor.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="HOXA11"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSBTAG00000014738","ENSECAG00000013229"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.4))
@ 
\caption{\genetreeexplanation{\textit{HOXA11}}}
\label{fig:hoxa11_evolution_tree}
\end{figure}

\begin{figure}
<<hbe1.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="HBE1"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSBTAG00000037815",
                                          "ENSMUSG00000078621"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=4,color="black",fontface="italic")+xlim(0,0.6))
@ 
\caption{\genetreeexplanation{\textit{HBE1}}}
\label{fig:hbe1_evolution_tree}
\end{figure}

\begin{figure}
<<nppb.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="NPPB"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.4))
@ 
\caption{\genetreeexplanation{\textit{NPPB}}}
\label{fig:nppb_evolution_tree}
\end{figure}

\begin{figure}
<<nppc.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="NPPC"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.32))
@ 
\caption{\genetreeexplanation{\textit{NPPC}}}
\label{fig:nppc_evolution_tree}
\end{figure}

\begin{figure}
<<galectins.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="LGALS1"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,1))
@ 
\caption{\genetreeexplanation{\textit{LGALS1} and \textit{LGALS2}}}
\label{fig:galectins_evolution_tree}
\end{figure}

\begin{figure}
<<lgals13.galectins.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="LGALS13"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,1.5))
@ 
\caption{\genetreeexplanation{\textit{LGALS13}}}
\label{fig:galectins_lgals13_evolution_tree}
\end{figure}

<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=NA,
                                    caption="\\lineagetableexplanationtypeiii{\\human}{all other species}",
                                    label="tab:huamn_linage_specific_all"
                                    )
setkey(hum.all.lin.spec,"Human Symbol")
@

>>>>

@@

\subsection{Common Species Terms}

<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=NA,
                                    caption="\\lineagetableexplanationtypeiii{\\human}{all other species}",
                                    label="tab:human_linage_specific_all"
                                    )
setkey(hum.all.lin.spec,"Human Symbol")
@

@@
